---
title: "DS6306 Case Study 1"
author: "Rick Fontenot"
date: "12/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this case study we assume that our audience is the CEO and CFO of Budweiser (our client) and that they only have had one class in statistics. They have hired us to answer 7 questions and beyond those general questions we will speculate / anticipate what may be of interest to them.

We will start by importing the following data for analysis:

Beers.csv:
Name: Name of the beer.
Beer_ID: Unique identifier of the beer.
ABV: Alcohol by volume of the beer.
IBU: International Bitterness Units of the beer.
Brewery_ID: Brewery id associated with the beer.
Style: Style of the beer.
Ounces: Ounces of beer.

Breweries.csv:
Brew_ID: Unique identifier of the brewery.
Name: Name of the brewery.
City: City where the brewery is located.
State: U.S. State where the brewery is located.

```{r}
library(dplyr)
library(tidyverse)

beers = read.csv("https://raw.githubusercontent.com/rickfontenot/DS6306_Study1/main/Beers.csv", header = TRUE)

breweries = read.csv("https://raw.githubusercontent.com/rickfontenot/DS6306_Study1/main/Breweries.csv", header = TRUE)


head(beers)
head(breweries)

#install.packages("visdat")
library(visdat)
vis_dat(beers, warn_large_data=FALSE)
vis_dat(breweries, warn_large_data=FALSE)

dim(beers) #2410 observations x 7 columns
dim(breweries) #558 observations x 4 columns

sum(is.na(beers$Brewery_id)) #there are no missing values on the merge var
sum(is.na(breweries$Brew_ID)) #there are no missing values on the merge var

beers <- beers %>% rename(Beer_Name = Name) #both dataframes have "Name"
breweries <- breweries %>% rename(Brewery_Name = Name)

beerbrew <- merge(beers,breweries, by.x = "Brewery_id", by.y = "Brew_ID")
head(beerbrew,6)
tail(beerbrew,6) # added to complete Question 2 
```


```{r, Joe's EDA}
#Joe EDA plotting on a map. 
#install.packages('usmap')
library(usmpa)
```


```{r, Joe's EDA, Question 1}
#Question 1 How many Breweries are in each state

#table of number of Breweries by state
st.brew <- table(beerbrew$State)

#visualize that table
beerbrew %>% ggplot(aes(x=State),color=State) + 
  geom_histogram(binwidth = 5, stat="count") +
  theme(axis.text.x=element_text(angle=45,size = rel(.8), 
        margin = margin(.05, unit = "cm"),vjust =.5))
```


```{r, Joe's EDA, Question 3}
#Question 3 Address Missing values in each col

colSums(is.na(beerbrew))

#ABV has 62 missing values
#IBU has 1005 missing values 2410 total 
#no other NAs found
#it is likely that different state differ on their requirement to track IBU and ABV to operate within that state.
```


```{r, Joe's EDA, Compute Median by state ABV and IBU}
#Question 4 compute median median abv and ibu
#i'm making the choice to omit given 1005 or 2410 na values

st.ibu <- aggregate(IBU~State, data =  beerbrew, median, na.action=na.omit)
st.ibu

###visualize the state IBU median
st.ibu %>% ggplot(aes(x=State,y=IBU, fill=IBU)) + scale_fill_distiller(palette='Spectral') + geom_bar(stat = "identity") +
  theme(axis.text.x=element_text(angle=45,size = rel(.8), 
        margin = margin(.05, unit = "cm"),vjust =.5, hjust = 1))


#by date median ABV omitted na values
#Here it is practical to impute the missing values
st.abv <- aggregate(ABV~State, data = beerbrew, median, na.action = na.omit)
st.abv

#visualize the state abv medians
st.abv %>% ggplot(aes(x=State,y=ABV, fill=ABV)) + scale_fill_distiller(palette='Spectral') + geom_bar(stat = "identity") +
  theme(axis.text.x=element_text(angle=45,size = rel(.8), 
        margin = margin(.05, unit = "cm"),vjust =.5, hjust = 1))

#x is a table filtered for the missing abv values.
x <- beerbrew[!complete.cases(beerbrew$ABV),]

```
```{r Joe's EDA, Question 5 which state has the highest abv /ibu}

max.abv <- max(beerbrew$ABV,na.rm = T)
max.abv

max.ibu <- max(beerbrew$IBU, na.rm = T)
max.ibu



```


